Thesis plan\\Version 1.1

### 2018-04-16 Thesis plan/Thesis plan.tex
update thesis plan v1.1

\title{Thesis plan\\Version 1.0}

@@

\item{Which parameter values create embeddings with the highest accuracy for academic texts?}

@@

@@

To answer the first research question, the optimal parameters for the embedding method have to be found. The comparison between embedding and TF-IDF must only be done with the optimal parameters for the embedding method.

@@

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The word-to-vec embedding method can have an higher accuracy or more utility\footnote{as in, reduced storing capacity and scalability to document/journal level} for academic texts than the TF-IDF algorithm.}
\item{The accuracy of academic embedding methods can be validated using classification tasks}
\end{itemize}
\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.

\subsection{Experiments:}
This research exists out of multiple experiments, the usage of the methods on two collections, one containing non-academic texts, while the other consists of academic texts. The results mentioned in this paragraph is the accuracy score on the categorization tasks. Each document in the test set will be labelled except for 20\%, these unlabelled documents have to be matched to the right set of documents. The correct matched percentage will be the result score for the algorithm/embedding method.\\
\paragraph{First experiment}The goal of the first experiment is to compare the results of my algorithm to earlier researches by comparing the results for the Wikipedia set\footnote{Which is also used in earlier researches}. This will ensure that the algorithm I use is comparable, and thus add legitimacy to the research. I expect that this is a small experiment, since it should only recreate already found results.\\
\paragraph{Second experiment}The second experiment is finding the optimal parameters for the set of academic papers. This will be done by fine-tuning the parameters in search for an optimal result, furthermore, the results of this process must be registered for comparison. This fine-tuning process is a calculation-intensive process, because of this, I expect that this experiment will take most of the time. This experiment also includes data gathering for the comparison of the methods.\\
\paragraph{Third experiment}The third experiment is creating the TF-IDF algorithm in the research environment and collecting data on its search results. This experiment will not take much time, since the TF-IDF is a simple algorithm to implement.\\
\paragraph{Comparison}
The final step is the comparison of the collected data from experiments 2 and 3, with this information, I will be able to accept or dismiss the hypothesis, and with that, answer the research questions.\\

@@

\section{Expected project results}
This research results in the following findings:
\begin{itemize}
\item{Comparison of multiple embedding validation methods for a collection of academic texts}
\subitem{- If possible, a best-to-use method}
\item{Validation of the hypothesis 'The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.'}
\subitem{- If these are related, an analysis of relationship in accuracy of the methods for the academic and non-academic texts.}
\end{itemize}
\section{Required expertise for this project}
This project requires:
\begin{itemize}
\item{Basic understanding of Machine Learning}
\item{Knowledge of Databricks/Spark (AWS)}
\item{Knowledge of embedding (methods \& evaluation)}
\item{SQL programming}
\item{Python programming}
\end{itemize}
\section{Timeline}
\begin{center}
\begin{tabular}{lll}
\textbf{Focus} & \textbf{Number of weeks} & \textbf{Date} \\
Setting up workspace & 1 & April 3 - April 6\\
Implementing methods & 2 & April 9 - April 20\\
Finding optimal & 3 & April 23 - May 11\\
embedding parameters & & \\
Data gathering experiment 1 & 1 & May 14 - May 18\\
Data gathering experiment 2 & 1 & May 21 - May 25\\
Writing & 2 & May 28 - June 8\\
Correction & 1 & June 11 - June 15\\
Submission & 1 & June 18 - June 22\\
Total & 12 & presentation date (NOT YET CONFIRMED) July 10\\
\end{tabular}\\
\end{center}
*  for non-academic texts\\ ** for academic texts

\section{Risks}
\begin{tabular}{ll}
\textbf{Risk} & \textbf{Prevention / Solution}\\
Unavailability of previously used & The dataset is already on an local PC\\datasets&\\&\\
Problems with implementing the& Elsevier has a range of experts on this topic,
\\methods&who are willing to help out if needed.\\&\\
Due to unforseen problems, there &The research consist of multiple hypothesis, atleast \\is not enough time to complete & one must be achievable\\the entire research &\\&\\
Student has a knowledge gab & I am taking an online course to understand basis of \\
 &Machine Learning and to get used to Databricks\\
\end{tabular}\\
\newpage
\section{Literature survey}
The literature survey provides the explanation of the embedding methods that will be compared in this research. Furthermore, they provide  non-academic texts\footnote{The papers contain references to publicly available sets that they used for their research.} that can be used to validate the implementation of the methods. This set will also be used to compare the non-academic texts to the academic texts.

>>>>

\title{Thesis plan\\Version 1.1}

@@

@@

\item{Which parameter values create embeddings with the highest accuracy for academic texts?\footnote{This research question will only be answered if there is sufficient time left}}

@@

@@

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The word-to-vec embedding method can have an higher accuracy or more utility\footnote{as in, reduced storing capacity and scalability to document/journal level} for academic texts than the TF-IDF algorithm.}
\item{The accuracy of academic embedding methods can be validated using classification tasks}
\end{itemize}
The utility will be measured by the vector size of the resulting representation, for word embeddings but also for the TF-IDF algorithm. Furthermore, the utility will be measured by the accuracy on higher level (article/journal) representation.

\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.

\subsection{Experiments:}
This research exists out of multiple experiments, the usage of the methods on two collections, one containing non-academic texts, while the other consists of academic texts. The results mentioned in this paragraph is the accuracy score on the categorization tasks. Each document in the test set will be labelled except for 20\%, these unlabelled documents have to be matched to the right set of documents. The correct matched percentage will be the result score for the algorithm/embedding method.\\
\paragraph{First experiment}The goal of the first experiment is to measure the accuracy of the (already present) word embeddings, and to collect the found accuracy results for the word embeddings.
\paragraph{Second experiment}The second experiment is creating the TF-IDF algorithm in the research environment and collecting data on its search results. This experiment will not take much time, since the TF-IDF is a simple algorithm to implement.\\
\paragraph{Comparison}
Thereafter, the the collected data from experiments 2 and 3 will be compared, with this information, I will be able to accept or dismiss the hypothesis, and with that, answer the research questions.\\
\paragraph{Third experiment}The third experiment is finding the optimal parameters for the set of academic papers. This will be done by fine-tuning the parameters in search for an optimal result, furthermore, the results of this process must be registered for comparison. This fine-tuning process is a calculation-intensive process, because of this, I expect that this experiment will take most of the time. This experiment also includes data gathering for the comparison of the methods.\\
\paragraph{Final comparison}
The final step is to compare the accuracy score of the obtained word-vectors to the results of the previous comparison. This will enable me to validate the remaining research question.

@@

\section{Expected project results}
This research results in the following findings:
\begin{itemize}
\item{Comparison of multiple embedding validation methods for a collection of academic texts}
\subitem{- If possible, a best-to-use method}
\item{Validation of the hypothesis 'The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.'}
\subitem{- If these are related, an analysis of relationship in accuracy of the methods for the academic and non-academic texts.}
\end{itemize}
\section{Required expertise for this project}
This project requires:
\begin{itemize}
\item{Basic understanding of Machine Learning}
\item{Knowledge of Databricks/Spark (AWS)}
\item{Knowledge of embedding (methods \& evaluation)}
\item{SQL programming}
\item{Python programming}
\end{itemize}
\section{Timeline}
\begin{center}
\begin{tabular}{lll}
\textbf{Focus} & \textbf{Number of weeks} & \textbf{Date} \\
Setting up workspace & 1 & April 3 - April 13\\
Initial validation set-up & 2 & April 16 - April 20\\
Applying validation methods to large scale set & 3 & April 23 - April 27\\
Data gathering experiment 1 & 1 & April 30 - May 4\\
Data gathering experiment 2 & 1 & May 7 - May 11\\
Comparison & 1 & May 14 - May 18\\
Data gathering experiment 3 & 2 & May 21 - June 1 \\
Comparison & 1 & June 4 - June 8\\
Finishing writing & 2 & June 11 - June 22\\
Total & 12 & presentation date, July 10\\
\end{tabular}\\
\end{center}
\section{Risks}
\begin{tabular}{ll}
\textbf{Risk} & \textbf{Prevention / Solution}\\
Unavailability of previously used & The dataset is already on an local PC\\datasets&\\&\\
Problems with implementing the& Elsevier has a range of experts on this topic,
\\methods&who are willing to help out if needed.\\&\\
Due to unforseen problems, there &The research consist of multiple hypothesis, atleast \\is not enough time to complete & one must be achievable\\the entire research &\\&\\
Student has a knowledge gab & I am taking an online course to understand basis of \\
 &Machine Learning and to get used to Databricks\\
\end{tabular}\\
\newpage
\section{Literature survey}
The literature survey provides the explanation of the embedding methods that will be compared in this research. Furthermore, they provide  non-academic texts\footnote{The papers contain references to publicly available sets that they used for their research.} that can be used to validate the implementation of the methods. This set will also be used to compare the non-academic texts to the academic texts.
